\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-06-01 paper/paper.tex
shuffle placement of figures, update plot
Add to paper, rethinking analysis of loss

\subsection{Model Comparisons}
\begin{figure}
\includegraphics[width=\textwidth]{fig/heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

@@

\begin{figure}[H]
    \centering
   \includegraphics[width=.8\textwidth]{fig/mod_compare_legend}
		\caption{Estimated GLFP for 4 Drive Brand Models plotted on Weibull paper.  Black step function is the truncated adjusted Kaplan Meier points.  \label{fig:first}} 
\end{figure}

@@

\subsection{Drive-model Comparisons}
We consider the problem of selecting between drive-models. From the
perspective of return on investment, is clear
that we should prefer the drive-models which will provide more years
of service. There are two sources of variation at play; the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{equation}

\end{equation}

>>>>

\subsection{Model Comparisons}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

\begin{figure}[H]
    \centering
   \includegraphics[width=\textwidth]{fig/mod_compare_legend}
		\caption{Estimated GLFP for 4 Drive Brand Models plotted on Weibull paper.  Black step function is the truncated adjusted Kaplan Meier points.  \label{fig:first}} 
\end{figure}

@@

\subsection{Drive-model Comparisons}
We consider the problem of ranking drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

There are two sources of variation at play; the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{equation*}
  p(t_{d,new}|t) = \int p(t_{d,new}|\theta_d) p(\theta_d|t) \, d\theta_d
\end{equation*}

We can sample from this distribution by drawing $t_{d,new}^{(s)}$ from
$\operatorname{GLFP}(\pi_d^{(s)},
\mu_1^{(s)},\sigma_1^{(s)},\mu_{2,d}^{(s)},\sigma_{2,d}^{(s)})$, for
$s=1,...,S$, using the saved posterior draws for the model
parameters. The expected time-to-failure (TTF) for drive-model $d$ can be estimated by
$$\frac{1}{S} \sum_{s=1}^{S} t_{d,new}^{(s)}.$$

While TTF is clearly important, due to the
anticipation of advancements in technology, we can expect that the
relative value of computer hardware will depreciate rather quickly. To account
for this, we can posit a model for this depreciation and instead of
TTF, we can consider the value at replacement. The IRS considered
computer hardware to be ``5-year'' equipment.(form 4562) Using``the declining
balance method'' the rate of depreciation is 40\% per year.

Let $L(t) = e^{-.4t}$ represent the value at the time of failure
relative to its original value. We can then define the predicted loss
of a unit as its value at time of failure.
